Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars

### 2018-08-20 main.tex
final draft updates for referee report 2

\subsubsection{Molecular Gas Content}
\label{sec:molecular gas content}
The molecular gas content of low-mass dwarf galaxies is generally assumed
to be small, but is not well constrained by either theory or observations. Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values. As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, just overlapping with this range. H$_2$ formation in our model is possible through formation on dust, the three body interaction, or the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$. The gas-phase reaction dominates in our low-metallicity galaxy over the other two channels by several orders of magnitude. In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$. Thus the presence of some ionizing background is required to generate the molecular fractions we find in our simulations, as confirmed in separate test simulations. \textbf{Our model does include a contribution from the meta-galactic background to the photodetachment of H$^{-}$. However, we note that we do not account for the contribution to this rate from the ISRF. We find that the H$_2$ fraction is more strongly dependent upon the Lyman-Werner radiation field, which is followed for each star, than the H$^{-}$ photodetachment rate. Our tests suggest that ignoring the stellar contribution to H$^{-}$ may lead to a 10--20\% overestimate in the computed H$_2$ fractions. This is discussed in more detail in Appendix~\ref{appendix:H minus}}.

In contrast, \citet{Hu2016} and \citet{Hu2017} find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$). However, although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field. Our model suggests that both H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies. Indeed it is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, though it is worth noting that the rate coefficients associated with gas-phase H$_2$ formation are still uncertain by an order of magnitude \citep{Glover2006,Glover2007}. Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays. It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}. This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.

@@

\setcounter{figure}{0}
\section{H$^{-}$ Photodetachment}
\label{appendix:H minus}
\textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations. Accounting for the photodetachment of H$_{-}$ from the stellar radiation field, which can dominate over the UVB,can be important for correctly modeling H$_2$ formation in low metallicity gas\citep{WolcottHaiman2012}. To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models\footnote{See the ``cooling_cell.py'' example here: https://grackle.readthedocs.io/en/grackle-3.1/Python.html} that iterates through the chemistry and cooling solvers with a constant density (10~cm$^{-3}$). In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background. As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate. In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left). A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{fH2.png}
\caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation. Each model is held at a uniform density $n = 10$~cm$^{-3}$. Each model varies either the H$^{-}$ photodetachment rate or the Lyman-Werner background over their respective UVB values by a given scale factor. Contours give factors of ten change in the H$_2$ fraction.}
\label{fig:Grackle grid}
\end{figure}

\textbf{H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV. For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction. Although we demonstrate that the H$_2$ fraction is more sensitive to the Lyman-Werner radiation field in our simulations, this radiation is dominated by short-lived massive stars and thus subject to fluctuations. Particularly in periods of no star formation, the regulation of H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation. Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars. Doing so in our current model, applying an optically thin 1/r$^2$ field for each star, would be computationally challenging for the dramatic increase in the number of stars below 8~M$_{\odot}$, our current radiation mass threshold.}

In addition, radiation from lower mass stars may be important in the is regime as the H$^{-}$ photodetachment threshold is low, or 0.76~eV. }

>>>>

\subsubsection{Molecular Gas Content}
\label{sec:molecular gas content}
The molecular gas content of low-mass dwarf galaxies is generally assumed
to be small, but is not well constrained by either theory or observations. Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values. As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, just overlapping with this range. H$_2$ formation in our model is possible through formation on dust, the three body interaction, or the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$. The gas-phase reaction dominates in our low-metallicity galaxy over the other two channels by several orders of magnitude. In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$. Thus the presence of some ionizing background is required to generate the molecular fractions we find in our simulations, as confirmed in separate test simulations.

In contrast, \citet{Hu2016} and \citet{Hu2017} find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$). However, although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field. Our model suggests that both H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies. Indeed it is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, though it is worth noting that the rate coefficients associated with gas-phase H$_2$ formation are still uncertain by an order of magnitude \citep{Glover2006,Glover2007}. Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.

\textbf{In addition, our model does not account for the stellar component of the radiation field that leads to H$^{-}$ photodetachment (E$_\gamma > 0.76$~eV), though we do account for the contribution from the UVB. We find that the H$_2$ fraction is more strongly dependent upon the Lyman-Werner radiation field, which is followed for each star, than the H$^{-}$ photodetachment rate. Our tests suggest that, by ignoring the stellar contribution to H$^{-}$ photodetachment, our results may represent upper limits on the H$_2$ mass. However, including this component will likely only make a substantial difference during periods of no star formation, when there are no massive stars with significant Lyman-Werner luminosities. We do not anticipate this to have a significant dynamical impact on our simulations, as is discussed in more detail in Appendix~\ref{appendix:H minus}}.

It is unclear how the combination of all of the above effects will behave, especially considering that, even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}. These uncertainties certainly warrant further study of molecular gas in low metallicity dwarf galaxies.

@@

\setcounter{figure}{0}
\section{H$^{-}$ Photodetachment}
\label{appendix:H minus}
%\textbf{This section is new:}

\textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations. Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, ca be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}. To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https:\/\/grackle.readthedocs.io\/en\/grackle-3.1\/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) for 200~Myr. In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background. As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate. In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left). A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{fH2.png}
\caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation. Each model is held at a uniform density $n = 10$~cm$^{-3}$. Each model varies either the H$^{-}$ photodetachment rate or the Lyman-Werner background over their respective UVB values by a given scale factor. Contours give factors of ten change in the H$_2$ fraction. We note the regime below 1.0 on each axis is somewhat unphysical, and is never reached in our hydrodynamics simulations.}
\label{fig:Grackle grid}
\end{figure}

\textbf{H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV. For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction. Although we demonstrate that the H$_2$ fraction is more sensitive to the Lyman-Werner radiation field in our simulations, this radiation is dominated by short-lived massive stars and thus subject to fluctuations. Particularly in periods of no star formation, the regulation of H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation. Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars. Doing so in our current model, applying an optically thin $1/R^2$ field for each star, would be computationally challenging due to the dramatic increase in the number of stars whose radiation would need to be tracked. }
